Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-09-01 Docs/Paper/LaTex/template.tex
3.2 Formal Model
7.3 Multi-core ESBMC with OpenMP using Binary Search

Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal ({\it i.e.}, system with hard real-time constraints). Based on Equations~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as 
%
\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|E_x| \leq S_0, 
\end{align}
%
\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard \textcolor{red}{\cite[p.~763]{Cormem}}.

@@

\textcolor{blue}{Precisas descrever no topo do algoritmo as entradas e saidas}
\textcolor{red}{The algorithm below is called from each worker in order to get the next step to execute if it exists, if not, zero or a negative number will be returned.}

>>>>

Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal ({\it i.e.}, system with hard real-time constraints). Based on Equations~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as 
%
\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|E_x| \leq S_0, 
\end{align}
%
\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.

@@

Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
